Speed and strength of an epidemic intervention

### 2020-06-19 doc/speedstrength.tex
added one citation
speed

@@

Here, we show that $r$ can also serve as a threshold, and also provide a useful metric for difficulty of elimination. We first generalize the idea that \RR\ measures the difficulty of elimination by showing we can measure an intervention's ``strength'' on the same scale as the reproductive number. 
We then show that we can likewise measure an intervention's ``speed'', and that there is a duality between the threshold $\RR=1$ and a corresponding minimal intervention strength required for elimination, and the threshold $r=0$ and a corresponding minimal intervention speed. 
We argue that the historical primacy of $\RR$ over $r$ is partly artificial, and discuss cases where strength provides the better framing for practical disease questions and cases where speed does.

>>>>

\section*{Significance statement}

The exponential growth rate $r$ (speed) and the reproductive number (strength) of an epidemic $\RR$ represent the speed and strength of an epidemic.
Even though both quantities have equally valid threshold values ($r=0$ and $\RR=1$) that determine whether a disease can spread in a population, disease modelers often measure the effectiveness of intervention by its ability to reduce $\RR$ below 1.
We generalize the classic, strength-based paradigm by defining the speed and strength of an intervention, which must be greater than their corresponding values of an epidemic to prevent its spread.
Both speed- and strength-based perspective can yield important, but different, biological insights into understanding the disease spread.

@@

Here, we show that $r$ can also serve as a threshold, and also provide a useful metric for difficulty of elimination (cf. \cite{ferretti2020quantifying}). We first generalize the idea that \RR\ measures the difficulty of elimination by showing we can measure an intervention's ``strength'' on the same scale as the reproductive number. 
We then show that we can likewise measure an intervention's ``speed'', and that there is a duality between the threshold $\RR=1$ and a corresponding minimal intervention strength required for elimination, and the threshold $r=0$ and a corresponding minimal intervention speed. 
We argue that the historical primacy of $\RR$ over $r$ is partly artificial, and discuss cases where strength provides the better framing for practical disease questions and cases where speed does.
